---
title: "supplement"
output: html_document
---

Here we will perform some sensitivity analysis upon the ODE model. 

```{r, echo=FALSE}

library(ggplot2)
library(deSolve)
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

## define useful names
kis4 <- bquote('k = 4 CTL' ^-1 ~'day' ^-1)
kis16 <- bquote('k = 16 CTL' ^-1 ~'day' ^-1)

size<-0.000001

saveODEdataAs<-"C:/Users/richard/Documents/PhD/0_PHD_PROJECTS/00_DirectKillingInsufficentForEL4RegressionInVivo/Rev1.0/data/odedata/odedata.csv"

raw <- read.csv('C:/Users/richard/Documents/PhD/0_PHD_PROJECTS/00_DirectKillingInsufficentForEL4RegressionInVivo/Rev1.0/data/mousedata/mousedata.csv')
names(raw) <- c('time','mouse','volume','id')
means<-read.csv('C:/Users/richard/Documents/PhD/0_PHD_PROJECTS/00_DirectKillingInsufficentForEL4RegressionInVivo/Rev1.0/data/mousedata/means.csv')
growthdata <- subset(means,group=='growth')
rawgrowth <- subset(raw,id=='growth') 
rawreg <- subset(raw,id=="regression")



## fit exponential growth

  ## log transform data
  growthdata$volume <- log(growthdata$volume)
  ## fit model
  model <- lm(growthdata$volume~growthdata$time)
  #transform data back
  growthdata$volume <- exp(growthdata$volume)
  
  ##transform model coefficidents
  intercept<-exp(as.numeric(coef(model)['(Intercept)']))
  slope <- as.numeric(coef(model)['growthdata$time'])
  model <- c(intercept,slope)
  
  #generate best fit line
  
  t<-seq(0,14,0.1)
  m<-model[1]*exp(t*model[2])
  

  
  odedata <- data.frame(time=t,volume=m,id=rep('ode model',length(t)))
  

  names(growthdata)[2]<-'id'
  
p <- ggplot(odedata, aes(x=time,y=volume/size,color=id,shape=id, linetype=id))+
  geom_line(size=1.5)+
  geom_point(data=rawgrowth,size=4)+
  scale_x_continuous(name="days after tumour injection",breaks=c(0,2,4,6,8,10,12,14))+
  scale_y_log10(name=bquote('number of tumour cells'), breaks=c(10^3,10^5,10^7,10^9),limits=c(10^3,10^9))+
  scale_colour_manual("id",values=c("red","black"),labels=c("measured in-vivo","model value"))+
  scale_linetype_manual("id",values=c(0,1),labels=c("measured in-vivo","model value"))+
  scale_shape_manual("id",values=c(16,NA),labels=c("measured in-vivo","model value"))+
 theme(text = element_text(size=20),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.title = element_blank(),legend.position=c(0.2,0.85),legend.key = element_blank())

plot(p)
  

# day 5
# day 10 10^7
# day 14 10^10

```
Our system equations are as follows:

T'=gT-kE
D'=kE-dD




```{r, echo=FALSE}

## since we assume a fixed form for our ctl density function, we have really only one parameter: that is Kden

killing <- function(t,Kden) {
  
  if (t<5)          pE    <-  0
  else if (t<7)     pE    <-  Kden*(t-5)
  else              pE    <-  2*Kden+2*Kden*(t-7)
  
  
  return(pE)
  }


 
Kden <- 0.01
t<-seq(0,14,0.1)
kE<-sapply(t,killing,Kden=Kden)

plot(t,kE)

```
For our ODE model with fixed Kden there are only three more available parameters:
k, g, and d. k is in fact subsumed into Kden. I.e. the killing term is kE(t) = k.kDen.(D+T).
So there are g and d. I believe we can keep g as constant and vary k or d, making a heatmap.

```{r, echo=FALSE}

ode.model <- function(Time, State, Pars) {
  with(as.list(c(State, Pars)), {
    
    TT<-State["T0"]
    D<-State["D0"]
    k<-Pars["k"]
    g <- Pars["g"]
    d<-Pars["d"]
    
    ## evaluate "killing term"
    ## killing per unit volume
    killing <- call("killing",Time,k)
    killing <- eval(killing)

    
    dT <- 0
    dD <- 0
    
    if(TT>0) {
      
      dT <- TT*g-(TT+D)*killing
      dD <- (TT+D)*killing -d*D
      
    }
    
    else dD <- -d*D
    
    return(list(c(dT,dD)))
  })
}


run.ode.sim <- function(i,sweep,base.pars,init.state,eval.times){
  base.pars[sweep]<-base.pars[sweep]*i
  out   <- data.frame(ode(init.state, eval.times, ode.model, base.pars,method="vode"))
  out$id <- rep(i,length(out$time))
  return(out)
}

get.turning.point <- function(sk,sd,sg,base.pars,init.state,eval.times){
    base.pars['k']<-base.pars['k']*sk
    base.pars['d']<-base.pars['d']*sd
    base.pars['g']<-base.pars['g']*sg
    out   <- data.frame(ode(init.state, eval.times, ode.model, base.pars,method="vode"))
    V <- as.numeric(out[,2]+out[,3])
    ti <- 14
    v.prev <- 0
    for(i in 1:length(V)){
      
      if(V[i]<v.prev){ ## turning point detector
        ti <- as.numeric(out[i,1])
        return(ti)
      }
      else v.prev <- V[i]
    }
    return(ti)
}

```

can sweep the k parameter - reproduces result that 10 fold increase in k*E/T needed for regression

```{r,echo=FALSE}
d<-2 
g<-0.86
eval.times <- seq(0,14,0.1)
rsweep <- c(1,4)
sweep<-"k"
ET7 <- 0.0125 ## known ratio of CTL to targets on day 7
kbase <- 4 ## kills/CTL/day

## scalings for k and d when making heatmap
sweep.sk <- (1:20)/2
sweep.d <- (1:20)/4

base.pars <-  c(k=kbase*ET7/2, d=d,  g=g) 
init.state  <- c(T0=1450,D0=0) 

sweep.results <- lapply(rsweep,function(i) run.ode.sim(i,sweep,base.pars,init.state,eval.times) )
sweep.results <- do.call(rbind,sweep.results)

sweep.pars <- expand.grid(sweep.sk,sweep.d)
names(sweep.pars) <- c('sk','sd')


tps <- sapply(1:length(sweep.pars[,1]), function(i) get.turning.point(sk=sweep.pars$sk[i],sd=sweep.pars$sd[i],sg=1,base.pars,init.state,eval.times) )

sweep.heatmap <- cbind(sweep.pars,tps)
sweep.heatmap$sk<-sweep.heatmap$sk
sweep.heatmap$sd<-sweep.heatmap$sd*d

sweep.subset <- subset(sweep.heatmap,(tps<10&tps>8))

```



```{r,echo=FALSE}

require(ggplot2)
alpha <- bquote(alpha)
deg.axis <- bquote('d '~'day' ^-1)

p <- ggplot(sweep.results,aes(x=time,y=(T0+D0),color=id,group=id))+
  geom_line(size=2)+
  scale_color_viridis_c('alpha')+
  scale_y_log10('total cells (D+T)')+
  scale_x_continuous('time')+
  theme_bw(base_size = 16)
p

p <- ggplot(sweep.heatmap,aes(x=sk,y=sd,fill=tps))+
  geom_tile()+
  geom_tile(data=sweep.subset,color="white")+
  geom_rect(aes(xmin = 4 - 0.25, xmax = 4 + 0.25, ymin = 2 - 0.25, ymax = 2 + 0.25),
               fill = "transparent", color = "red", size = 1.5)+
  geom_rect(aes(xmin = 1 - 0.25, xmax = 1 + 0.25, ymin = 2 - 0.25, ymax = 2 + 0.25),
               fill = "transparent", color = "red", size = 1.5)+
  scale_fill_viridis_c('turning point')+
  scale_x_continuous(alpha)+scale_y_continuous(deg.axis)+
  theme_classic(base_size = 16)
p

```



```{r, echo=FALSE}
data <- data.frame(time=t,density=d,id=rep('assumed',length(t)))
mdens<-data.frame(time=c(7,8),density=c(13040,25050),id=c('measured','measured'))

p <- ggplot(data, aes(x=time,y=density*size,color=id,shape=id, linetype=id))+
  geom_line(size=1.5)+
  geom_point(data=mdens,size=4)+
  scale_x_continuous(name="days after tumour injection",breaks=c(0,2,4,6,8,10,12,14))+
  scale_y_continuous(name=bquote('Effector:Target ratio'))+
  scale_colour_manual("id",values=c("black","red"),labels=c("model value","measured in-vivo"))+
  scale_linetype_manual("id",values=c(1,0),labels=c("model value","measured in-vivo"))+
  scale_shape_manual("id",values=c(NA,16),labels=c("model value","measured in-vivo"))+
 theme(text = element_text(size=20),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.title = element_blank(),legend.position=c(0.2,0.9),legend.key = element_blank())

plot(p)
  


```



FIg 1c)

```{r, echo=FALSE}

size<-0.000001
times <- seq(0, 14, by = 0.05) 

## exponential parameters

pars_e  <- c(alpha   = 0.859,
           deg = 2.77,  
           k=4,
           a1=6520,
           a2=12010, 
           pE2=13040,
           pE3=25050,
           tumor_cellsize=size) 

ini_e  <- c(T0=0.001448793/size,D0=0) 

out   <- ode(ini_e, times, ode.model, pars_e,method="vode")
v_e<-rowSums(out[,2:3]*size)

pars_e['k']<-16
out   <- ode(ini_e, times, ode.model, pars_e,method="vode")
k16 <- rowSums(out[,2:3]*size)

density <- sapply(times,ctld,Pars=pars)
tcells4<-density*v_e
tcells16<-density*k16


num4=data.frame(time=times,number=tcells4,id=rep("k =  4",length(times)))
num16=data.frame(time=times,number=tcells16,id=rep("k = 16",length(times)))
num=rbind(num4,num16)

data4 <- data.frame(time=times,volume=v_e,id=rep("k =  4",length(times)))
data16 <- data.frame(time=times,volume=k16,id=rep("k = 16",length(times)))
data<-rbind(data4,data16)

## write ODE data to file for comparison in ABM figure




  growthdata <- subset(means,group=='regression')
  names(growthdata)[2]<-'id'
  
#tst <- rawreg[,c(1,3,4)]


#tst <- rbind(data,tst)

data$volume<-data$volume/size

pw <- ggplot(data, aes(x=time))+
  geom_line(size=1.5,aes(color=id,y=volume))+
  geom_point(data=rawreg,aes(x=time,y=volume*10^6,shape="transfer data"),size=4)+
  scale_x_continuous(name="days after tumour injection",breaks=c(0,2,4,6,8,10,12,14))+
  scale_y_log10(name=bquote('number of tumour cells'), breaks=c(10^3,10^5,10^7,10^9),limits=c(10^2,10^9))+
  scale_colour_manual("id",values=cbbPalette[-1],labels=c(kis4,kis16))+
 scale_shape_manual(values = c(17))+

  theme(text = element_text(size=20),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.title = element_blank(),legend.position=c(0.2,0.80),legend.key = element_blank())

plot(pw)

  p <- ggplot(num, aes(x=time,y=number,color=id))+
  geom_line(size=1.5)+
  scale_x_continuous(name="days after tumour injection",breaks=c(0,2,4,6,8,10,12,14))+
  scale_y_log10(name="number of intratumoural CTLs",breaks=c(10^2,10^4,10^6))+
  scale_colour_manual("id",values=cbbPalette[-1],labels=c(kis4,kis16))+
 theme(text = element_text(size=20),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.title = element_blank(),legend.position=c(0.2,0.80),legend.key = element_blank())

plot(p)

density <- as.numeric(sapply(as.numeric(data$time),ctld,Pars=pars))
tcells <- as.numeric(density*data$volume )
data<-cbind(data,density,tcells)
data$volume<-data$volume


write.csv(data,saveODEdataAs,row.names = FALSE)

```

```{r, echo=FALSE}

size<-0.000001
times <- seq(0, 14, by = 0.05) 

## exponential parameters

pars_e  <- c(alpha   = 0.859,
           deg = 100,  
           k=4,
           a1=6520,
           a2=12010, 
           pE2=13040,
           pE3=25050,
           tumor_cellsize=size) 

ini_e  <- c(T0=0.001448793/size,D0=0) 

out   <- ode(ini_e, times, ode.model, pars_e,method="vode")
v_e<-rowSums(out[,2:3]*size)

pars_e['k']<-16
out   <- ode(ini_e, times, ode.model, pars_e,method="vode")
k16 <- rowSums(out[,2:3]*size)

density <- sapply(times,ctld,Pars=pars)
tcells4<-density*v_e
tcells16<-density*k16


num4=data.frame(time=times,number=tcells4,id=rep("k =  4",length(times)))
num16=data.frame(time=times,number=tcells16,id=rep("k = 16",length(times)))
num=rbind(num4,num16)

data4 <- data.frame(time=times,volume=v_e,id=rep("k =  4",length(times)))
data16 <- data.frame(time=times,volume=k16,id=rep("k = 16",length(times)))
data<-rbind(data4,data16)

## write ODE data to file for comparison in ABM figure



  means<-read.csv('E:/figures/plotdata/mousedata/means.csv')
  growthdata <- subset(means,group=='regression')
  names(growthdata)[2]<-'id'
  
tst <- rawreg[,c(1,3,4)]


tst <- rbind(data,tst)

tst$volume<-tst$volume/size

pw <- ggplot(tst, aes(x=time,y=volume,color=id,shape=id, linetype=id))+
  geom_line(size=1.5)+
  geom_point(size=4)+
  scale_x_continuous(name="days after tumour injection",breaks=c(0,2,4,6,8,10,12,14))+
  scale_y_log10(name=bquote('tumour cell count'), breaks=c(10^3,10^4, 10^5,10^6,10^7,10^8,10^9),limits=c(10^2,10^9))+
  scale_colour_manual("id",values=c("navyblue","darkgreen","red"),labels=c("k =  4","k = 16","measured in-vivo"))+
  scale_linetype_manual("id",values=c(1,1,0),labels=c("k =  4","k = 16","measured in-vivo"))+
  scale_shape_manual("id",values=c(NA,NA,16),labels=c("k =  4","k = 16","measured in-vivo"))+
  theme(text = element_text(size=20),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.title = element_blank(),legend.position=c(0.15,0.90),legend.key = element_blank())

plot(pw)

  p <- ggplot(num, aes(x=time,y=number,color=id,linetype=id))+
  geom_line(size=1.5)+
  
  scale_x_continuous(name="days after tumour injection",breaks=c(0,2,4,6,8,10,12,14))+
  scale_y_log10(name="Number of T cells")+
  scale_colour_manual("id",values=c("navyblue","darkgreen"),labels=c("k =  4","k = 16"))+
  scale_linetype_manual("id",values=c(1,1),labels=c("k =  4","k = 16"))+

 theme(text = element_text(size=20),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.title = element_blank(),legend.position=c(0.15,0.90),legend.key = element_blank())

plot(p)

density <- as.numeric(sapply(as.numeric(data$time),ctld,Pars=pars))
tcells <- as.numeric(density*data$volume )
data<-cbind(data,density,tcells)

data$volume<-data$volume/size
write.csv(data,"E:/figures/plotdata/f1/data.csv",row.names = FALSE)

```